
\cvsection{Projects}

\begin{cventries}

  \cventry
    {Full-Stack Programming}
    {Software Repository website}
    {2nd year University Small Enterprise Team Project}
    {Jan. 2025 - Apr. 2025}
    {
      \begin{cvitems} 
        \item{Conducted in an agile scrum group of 8 student developers to create a product for a real client.}
        \item{Created a fully functioning role-based access-controlled website with a backend database to store details of all software used in a system.}
        \item {Incorporated a full stack of Java, Docker, SpringBoot with configured Spring security, React, JavaScript, HTML, and CSS.}
        \item {Added secure, encrypted username and password system with working JWT, using SpringSecurity.}
        \item{Used HTML and CSS web design to create aesthetic and functioning webpages for the frontend.}
      \end{cvitems}
    }

    \vspace{3mm}
    
    \cventry
    {Robotics Programming}
    {Java LeJos Robot}
    {1st year University Team Project}
    {Jan. 2024 - Apr. 2024}
    {
    \begin{cvitems}
        \item{Programmed and built a robot that reads and plays sheet music.}
        \item{Developed in a group of 4 students to gain experience with techniques used in coding robotics.}
        \item{Implemented using Python and the leJOS framework, which ran on Java threading.}
    \end{cvitems}
    }

    \vspace{3mm}

    \cventry
    {Application Development}
    {Shop MFD(Multi-Functional Device) app}
    {A-level NEA}
    {Jan. 2023 - May. 2023}
    {
    \begin{cvitems}
        \item {Self-directed project to create and showcase capabilities as a programmer at a KS5 level.}
        \item {Used Python and SQL database.}
        \item {Created a shop assistant app for picking deliveries, item lookup, and off-sales.}
    \end{cvitems}
    }
    
    
\end{cventries}
